Type Refinements for the Working Class

### 2015-11-12 paper.tex
"the the"
missing word

  In other words, the hypothetical judgment
  $\HypJ{\mathcal{J}_2}{\mathcal{J}_1}$ is evident when there shall forevermore
  be an effective transformation of evidence for the antecedent into evidence
  for the consequent. It is important to keep in mind that this is a
  \emph{semantic} consequence and therefore expresses admissibilities, in
  contrast to the the \emph{logical} consequence which expresses derivabilities
  \cite{harper:2016}.  We will not have any need for the latter.
\end{definition}

After this section, we will define a judgment either by rules, or by an
informal semantical explanation, in both cases leaving its intensional
character implicit. A judgment will said to be \emph{correct} or \emph{valid}
in case it is globally inhabited.

>>>>

  In other words, the hypothetical judgment
  $\HypJ{\mathcal{J}_2}{\mathcal{J}_1}$ is evident when there shall forevermore
  be an effective transformation of evidence for the antecedent into evidence
  for the consequent. It is important to keep in mind that this is a
  \emph{semantic} consequence and therefore expresses admissibilities, in
  contrast to the \emph{logical} consequence which expresses derivabilities
  \cite{harper:2016}.  We will not have any need for the latter.
\end{definition}

After this section, we will define a judgment either by rules, or by an
informal semantical explanation, in both cases leaving its intensional
character implicit. A judgment is said to be \emph{correct} or \emph{valid}
just in case it is globally inhabited.
